---
title: "Weight of Fish"
author: "Michael Maida"
date: "Fall 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(leaps)
library(car)
mydata <- read.csv(file = "Fish.csv")
perch <- filter(mydata, Species == "Perch")
perch <- select(perch, -Species)
pike <- filter(mydata, Species == "Pike")
pike <- select(pike, -Species)
roach <- filter(mydata, Species == "Roach")
roach <- select(roach, -Species)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

In this report, we are given data that describes the different characteristics of three different fish: Perch, Pike, and Roach. This report attempts to analyze what characteristic is the greatest predictor of these different fishes' weights by value of adjusted R-squared. We will accomplish this via a regression model.

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

To conduct graphical analysis, and adjusted R-square graph (AdjR^2) was created. This illustrated which combinations of variables resulted in the greatest adjusted R-squared value. Next, summary functions were called to show the numerical descriptive analysis, including the p-values and Adjusted R-squared values.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

First, a data set named "perch" was created that includes 6 different numerical variables: Weight, Length1, Length2, Length3, Height, and Width.

A function was then called to run the different combinations of the variables and assort them in order of greatest to least R-Squared value on a 2-dimensional graph.

```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

This data can be further verified. The following function indicates which combination yielded the greatest R-squared value, and the second function indicated which variables were used in that data set.

```{r}
which.max(summary.out$adjr2)
summary.out$which[2,]
```

This experiment is repeated with Pike and Roach, in that order.

```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
which.max(summary.out$adjr2)
summary.out$which[5,]
```

```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
which.max(summary.out$adjr2)
summary.out$which[2,]
```

Graphically, these show that Length1, Length2, Length3, Width, and Height yield the greatest R-squared for Pike, and Length3 and Width yield the greatest R-squared for Roach.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

A summary function is called for the Perch.

```{r}
best.model <- lm(Weight~Height+Width,data=perch)
summary(best.model)
```

This indicates that the greatest adjusted R-squared achievable is 0.94 with Height and Width.

A summary function is called for the Pike.

```{r}
best.model2 <- lm(Weight~Length1+Length2+Length3+Width+Height, data=pike)
summary(best.model2)
```

This indicates that the greatest adjusted R-squared achievable is 0.98 with all 5 variables: Length1, Length2, Length3, width, and height.

Finally, a summary function is called for the Roach.

```{r}
best.model3 <- lm(Weight~Length3+Width, data=roach)
summary(best.model3)
```

This shows that the greatest adjusted R-squared achievable is 0.85 by using Length3 + Width.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

The hypothesis stated that we can use 2 predictor variables to predict the weight of Perch. The two values, Height and Width, succeeded in predicting the weight of the Perch. The P-value was less than 2.2e-16, or 0.0000000000000002, and the adjusted R-squared was 0.94. Because these two values were so successful in their prediction, we accept the hypothesis and, by definition, reject the null hypothesis that no two of the predictor variables could predict the weight of the Perch.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We reject the null hypothesis; Height and Width succeeded greatly in predicting the weight of the Perch. Similarly, the predictor values of Length1, Length2, Length3, Width, and Height could predict the weight of the Pike while the Length3 and Width could predict the weight of the Roach, albeit to a lesser degree. The common variable between the three is Width, which makes intuitive sense; the larger a creature is, the more fat is stored on the side to make it wider. 
